---
title: 'Your title'
subtitle: 'Conference / Panel name'
author: 'Philipp Kleer'
institute: 'Department of Political Science | Justus-Liebig-University Giessen' 
# User socials
mastodon: 'philk'
mastodonurl: 'https://polsci.social/@'
bluesky: 'phil-k'
#twitterx: '_philk'
git: 'bpkleer'
orcid: '0000-0003-1935-387X'
lattes: '4785970328498860'
# researchgate: 'Philipp-Kleer'
contactemail: 'philipp.kleer+contact@posteo.com'
contactsite: 'https://bpkleer.github.io/en'
qrcode: '{{< qrcode https://bpkleer.github.io qr-start colorDark="#5A5A5A" >}}'
# Settings
date: 'Report Last Run: `r Sys.time()`'
date-format: long
bibliography: assets/lit.bib
csl: assets/apa.csl
format: 
  revealjs: default
revealjs-plugins:
  - simplemenu
editor: source
---

```{r}
#| label: setup-libraries-data
#| include: false
#| message: false

library(tidyverse)
library(knitr)
library(kableExtra)

myhelpers::load_slidecols()
```

# Quarto {data-stack-name='Preparations' }

{{< brand color.palette.style1 >}}


## add extras in positron


You need to add extensions manually:

- `quarto install extension sellorm/quarto-social-embeds`
- `quarto install extension schochastics/academicons`
- `quarto add martinomagnifico/quarto-simplemenu`
- `quarto add mcanouil/quarto-iconify`
- `quarto add quarto-ext/fontawesome`
- `quarto install extension jmbuhr/quarto-qrcode`

## Create variables
You can upfront create variables that can be used in the following

```{python}
#| tags: [parameters]

name = 'Philipp'
data_filte = '2012'
```

# Motivation {data-stack-name='Start'}

... and what we already know {{< iconify emojione-monotone books size=2x >}} 

## Why?

Explain why it is interesting to research the problem (few references to theory, audience knows; 2-3 key pieces!)

## Empirical evidence

Reference briefly other research, if questions on this, you can come back on this in the discussion

# Data & Methods {data-stack-name='Data'}

What we used {{< iconify icon-park-twotone data-two size=2x >}} and how we did it {{< iconify fluent-mdl2 test-plan size=2x >}} 

## Data
Lorem ipsum

## Analytical strategy
Here explain what you did and why you did this

{{< iconify mdi wrench-settings-outline size=xl >}} check and control differences/similarities

{{< iconify material-symbols low-priority-rounded size=xl >}} using knowledge from general population

{{< iconify solar danger-triangle-bold-duotone size=xl >}} restricted model due to comparability across data sets

{{< iconify ph number-circle-one-duotone size=xl >}} Step 1

. . .

{{< iconify ph number-circle-two-duotone size=xl >}} Step 2

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;a) HTML space for intendation

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;b) HTML space for intendation

. . .

{{< iconify ph number-circle-three-duotone size=xl >}} Step 3

## Tricks and Ruses

How we made it work {{< iconify majesticons settings-cog-check-line >}}.

Probably not necessary, only use if you had to do something that is not really common. Explain why you did so and why it is a good approach (reference work others)

### Include Tikz
```{r, engine = 'tikz'}
\begin{tikzpicture}
 \draw (0,0) circle (1cm);
 %\pause
 \draw (0,0) circle (2cm);
\end{tikzpicture}
```

## Operationalization

I would skip this to the extras. 

# Results {data-stack-name="Results"}

... what we found in the data {{< iconify icon-park-twotone find size=2x >}}

## First results

{{< iconify icon-park-twotone difference-set size=xl >}} Differences

{{< iconify pajamas search-results size=xl >}} global model fit

{{< iconify pepicons-print equal-circle-filled size=xl >}} equal 

{{< iconify pajamas comparison size=xl >}} similar

# {{< iconify icon-park-outline bye >}} Goodbye {.goodbye data-state='hide-menubar'}

[Please, shoot questions at me. {{< iconify ph person-simple-throw-fill size=xl >}}]{.greetings} [If you use citations, put  before \@ in usernames]{.greetings}

::: qrcode-final
{{< fa regular person-chalkboard size=Huge >}} {{< qrcode https://bpkleer.github.io qr-end colorDark='#5A5A5A' >}}
:::

::: social

[{{< fa brands mastodon >}}](https://polsci.social/@philk){.mastodon} [\@philk](https://polsci.social/@philk) \| [{{< fa solid square >}}](https://bsky.app/profile/phil-k.bsky.social){.bluesky} [\@phil-k](https://bsky.app/profile/phil-k.bsky.social) \| [{{< fa brands github >}}](https://github.com/bpkleer){.github} [bpkleer](https://github.com/bpkleer)

[{{< ai orcid >}}](https://orcid.org/0000-0003-1935-387X){.orcid} [0000-0003-1935-387X](https://orcid.org/0000-0003-1935-387X) \| [{{< ai lattes >}}](http://lattes.cnpq.br/4785970328498860){.lattes} [4785970328498860](http://lattes.cnpq.br/4785970328498860) 

[{{< fa envelope >}}](mailto:philipp.kleer+contact@posteo.com){.email}[ philipp.kleer+academia@posteo.com](mailto:philipp.kleer+contact@posteo.com) \| [{{< fa globe >}}](https://bpkleer.github.io){.website}[ bpkleer.github.io](https://bpkleer.github.io)
:::

::: footer
:::

## References {visibility='uncounted'}

::: {#refs}
:::

# Extras {visibility='uncounted' data-state='hide-menubar'}

What we couldn't fit into 12 minutes {{< iconify pepicons-print loop-plus size=xl >}}

## Operationalization 
